\newpage
\addcontentsline{toc}{chapter}{REFERENCES}
\begin{thebibliography}{99}
	\bibitem{1} "PhishHaven—An Efficient Real-Time AI Phishing URLs Detection System" ( Maria Sameen, Kyunghyun Han, Seong Oun Hwang [2020])
	
	\bibitem{2}
	"Sufficiency of Ensemble Machine Learning Methods for Phishing Websites Detection"
	(Yi Wei, Yuji Sekiya. [2021])
	
	\bibitem{3}
	"Eth-PSD: A Machine Learning-Based Phishing Scam Detection Approach in Ethereum" (Arkan Hammoodi Hasan Kabla, Mohammed Anbar, Selvakumar Manickam, Shankar Karupayah
. [2021])
	
	\bibitem{4}
	"OFS-NN: An Effective Phishing Websites Detection Model Based on Optimal Feature Selection and Neural Network" (Erzhou Zhu, Yuyang Chen, Chengcheng Ye, Xuejun Li, Feng Liu. [2019])
	
	\bibitem{5}
	"Comparison of Classification Algorithms for Detection of Phishing Websites" (Paulius Vaitkevicius. [2020])
	
	\bibitem{6}
	"Phishing Detection using Random Forest, SVM and Neural Network with Backpropagation" (Sindhu, Sunil Parameshwar Patil, Arya Sreevalsan,  Faiz Rahman	[2020])
	
	\bibitem{7}
	"Intelligent rule-based phishing websites classification" (Rami M. Mohammad, Fadi Thabtah, Lee McLusky. [2014])
	
	\bibitem{8}
	"Phishing sites detection based on Url Correlation" (Ying Xue, Yang Li,Yuangang Yao, Xianghui Zhao, Jianyi Liu,Ru Zhang. [2016])
	\bibitem{9}
	"Characteristics of Understanding URLs and Domain Names Features: The Detection of Phishing Websites With Machine Learning Methods" (Ilker Kara, Murathan Ok, Ahmet Ozaday
. [2022])
	\bibitem{10}
	"Detecting phishing websites using machine learning technique" (Ashit Kumar Dutta, Zhihan Lv. [2018])
	\bibitem{11}
	"Web Phishing Detection Using Machine Learning " (N Kumaran, Purandhar Sri Sai, Lokesh Manikanta. [2022])
	\bibitem{12}
	"Detection of Phishing Websites using Machine Learning" (Atharva Deshpande, Omkar Pedamkar, Nachiket Chaudhary . [2021])
	\bibitem{13}
	A New Method for Detection of Phishing Websites: URL Detection" (Shraddha Parekh,
Dhwanil Parikh ,
Srushti Kotak , Prof. Smita Sankhe. [2018])
	\bibitem{8}
	"Detection of URL based Phishing attacks Using Machine Learning" (Ms. Sophiya Shikalgar , Dr. S. D. Sawarkar , Mrs. Swati Narwane. [2018])
	\bibitem{8}
	"Large-Scale Automatic Classification of Phishing Pages 
" (Collin Whittaker, Brian Ryner, Maria Nasif. [2010])





\end{thebibliography}


